Data Provenance Tracking for Concurrent Programs

### 2014-09-03 paper.tex
added octet discussion.  back on 11

\newcount\draft\draft=1 % set to 0 for submission or publication
\newcount\cameraready\cameraready=0

@@

\paragraph{Communication and Sharing Analyses}
Several techniques have been proposed analyze dependences and communication in
concurrent programs.  A closely related recent effort on dynamic dependence
analysis is Octet~\cite{octet}, which captures inter-thread communication
soundly and to aid in building arbitrary concurrency analyses. Octet tracks the
``locality state'' of memory locations to make dependence tracking efficient.
Octet differs from \ctraps in that it focuses on soundness, was built primarily
to optimize dependence tracking, and does not discuss direct use of dependence
information to help with debugging.  Octet's average run time overhead (26\%)
is comparable to the overhead of both \lws and \ctraps and Octet, \lws, and
\ctraps all have low enough overheads for production use in many cases.

>>>>

\newcount\draft\draft=0 % set to 0 for submission or publication
\newcount\cameraready\cameraready=0

@@

\paragraph{Communication and Sharing Analyses}
Several techniques have been proposed analyze communication in concurrent
programs and are especially related to \ctraps.

A closely related recent effort on dynamic dependence analysis is
Octet~\cite{octet}, which exposes inter-thread communication soundly to
concurrency analyses.   Octet reports an average run time overhead of 26\%,
which is comparable to the overhead of \lws and \ctraps.

To acheive these low performance overheads, Octet makes fundamental assumptions
about its target system that \lws and \ctraps do not make.  To track
communication, a thread in Octet must stop at ``safe points'' in an execution.
At a safe point, the thread executes extra code to check a message queue that
reports communication with other threads.  Octet assumes safe points at loop
back edges, method entries, and blocking function calls.  This assumption is
reasonable for Java, as many Java VMs use safe points to implement GC.  Octet
uses existing safe points and their performance baseline assumes a VM with
existing instrumentation at such safe points.  In contrast, C/C++ programs do
not have a VM or existing safe points.   Checking a queue on every function
call and method entry is likely to impose a higher performance penalty than
Octet saw in Java.  \lws keeps overheads practical by relying on program
synchronization to keep dependence information consistent --- unlike Octet
which is always sound, Data-races may leave \lws data inconsistent.  However,
\lws need not pay the cost of safe points and message queue checks.

Another important difference between Octet and this work is that this work
illustrates the benefit of directly using \lws's provenance information for
debugging.   Octet does not explore provenance debugging.
